%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graphics Programming Engineer Intern} % Job title
    {Viga Entertainment Technology} % Organization
    {Dec 2021 - Feb 2022} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed full body motion capture pipeline and 3D facial reconstruction pipeline.}
        \item {Implemented state of the art motion capture system to capture detailed human motion including muscle deformation.}
        \item {Applied a neural network based pipeline using TensorFlow to extract key-points from a series of frames.}
        \item {Utilized optimization methods to fit statistical human body models to extracted points to capture fine details.}
        \item {Implemented a pipeline to construct detailed 3D model of human faces from stereo images.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Product Development Intern} % Job title
    {Smerkato} % Organization
    {Sept 2021 - Oct 2021} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed the seller-side app for a B2B e-commerce company.}
        \item {Used Flutter to develop application for android and IOS devices using Firebase as the backend.}
        \item {Application aimed to facilitate onboarding of sellers, listing products, tracking orders and delivering insights.}
        \item {Integrated Firebase (Authentication, Firestore and Storage), Google Maps and Geolocator APIs into the app.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
