%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Positions of Responsibility}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Computer Graphics Society} % Job title
    {Head of Research and Development} % Organization
    {Jan 2021 - July 2022} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Headed the Research and Development team of the Computer Graphics and Game Development Society of IIT Kharagpur.}
        \item {Contributed to and managed projects on various topics such as Simulations, Computer Vision and Game Development.}
        \item {Collaborated with Technology Students Gymkhana to conduct Open-IIT Game and Graphics Development Workshop.}
        \item {Contributed towards areas such as Development of Games, Youtube Video production, and Recruitment of Junior members.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Awaaz, IIT Kharagpur} % Job title
    {Senior Reporter} % Organization
    {August 2019 - July 2021} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Part of a team of reporters working towards bringing news and information about the institute to the student fraternity.}
        \item {Organised an annual event, "Panch Parmeshwar" during Spring Fest with a footfall of almost 300 people.}
        \item {Ensured proper coverage of campus issues concerning student welfare, such as those relating to mess and fees.}
        \item {As a part of the design team, created Infographics and Posters using Adobe Photoshop and Illustrator.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
