%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Term Project for Evolutionary Algoriths course} % Job title
    {Evolutionary Algorithm based Self Learning AI} % Organization
    {Jan 2021 - April 2021} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Employed Evolutionary Algorithms for training AI-controlled teams to play in 3-a-side football matches.}
        \item {Implemented a feed-forward neural network in C# and used it to model the AI's response to the match situation.}
        \item {Used Genetic Algorithm to train the Neural-Network by competing against other AI-controlled teams for 100 generations.}
        \item {Players reached 85 percent of the maximum possible fitness score while the average goals per match increased by four times.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Hobby Project} % Job title
    {Erosion Simulation for Procedural Terrain Generation} % Organization
    {Jan 2021 - June 2021} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Simulated the effect of water and heat on the landscape to generate realistic-looking terrain.}
        \item {Implemented a research paper on real-time fluid simulation to replicate the motion of water on Earth's surface.}
        \item {Employed GPU based parallelization of the algorithm for processing the simulation at interactive frame rates.}
        \item {Implemented mesh and texture generation algorithms in C# to generate a 3D visualisation of the simulation result.}
        \item {Simulation results successfully reproduced real-life features such as mountain ridges, river valleys, and flood plains.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Term Project for Work-System Design Course} % Job title
    {VR Application for Mental Health Improvement} % Organization
    {Jan 2021 - Apr 2021} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a relaxing Virtual Reality environment to improve the mental health of the user}
        \item {Developed a Virtual Reality environment of a forest scene using Unity Engine to reduce the user's stress and fatigue.}
        \item {Implemented Guided Meditation feature to allow the user to listen to a guide's voice and perform meditative exercises.}
        \item {Used C# to script the behavior of the app, Blender to 3D model the scene and Adobe Illustrator to create textures.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {2D platformer video game for Android Devices} % Job title
    {Ricksy Run} % Organization
    {Dec 2019 - Feb 2020} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an Android Game using Unity Engine and deployed it on the Google Play Store, gaining 15000+ downloads.}
        \item {Used Google Firebase Authentication and Realtime Database APIs to implement a global leaderboard feature.}
        \item {Programmed game behaviour using C#, and integrated Google Ads using Admob API for revenue generation.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
